\section{Introduction}

The field of very-high-energy (VHE) astronomy is growing tremendously – while only a decade ago we observed no more than a handful of sources in the GeV range, today we have thousands, including hundreds within the TeV range. This advancement has been made possible due to our novel ground-based Cherenkov telescope instruments. Such systems exhibit more accurate source detections and higher angular resolutions than ever before. Space-based satellites sharing similar technological breakthroughs have further developed the high-energy (HE) range of gamma-ray astronomy, as can be observed in the latest images from the Fermi Large Area Telescope (Fermi-LAT). As a whole, the instruments can capture gamma-rays in a wide spectrum of energies from 10 MeV to 10 TeV. The High Energy Stereoscopic System (H.E.S.S.) Galactic Plane Survey \cite{hgps}, the High-Altitude Water Cherenkov Observatory (HAWC) 1st Year Catalog, and the fourth Fermi-LAT Point Source Catalog (4FGL) are among the highly anticipated surveys that will be unveiled in the near future. Furthermore, with an incoming wave of notable systems planned to operate soon, such as the ground-based Cherenkov Telescope Array (CTA), we expect to discover numerous never-before-seen sources in the gamma-ray sky. With such abundance of HE and VHE sources and a rapid growth of interest in gamma-ray astronomy, there is an increasingly evident need for a central hub of all relevant catalog and image data. Our website (\url{http://gamma-sky.net}) was designed to function as such.

% TODO: make sure these references are put in the appropriate places:
%
% \begin{itemize}
%     \item \cite{tevcat} -- TeVCat: An online catalog for Very High Energy Gamma-Ray Astronomy (\url{http://tevcat.uchicago.edu/})
%     \item \cite{tgevcat} -- The Very High Energy source catalog at the ASI Science Data Center (\url{http://www.asdc.asi.it/tgevcat/})
%     \item \cite{3fgl} -- Fermi Large Area Telescope Third Source Catalog
%     \item \cite{2fhl} -- 2FHL: The Second Catalog of Hard Fermi-LAT Sources
%     \item \cite{snrcat} -- A census of high-energy observations of Galactic supernova remnants (\url{http://www.physics.umanitoba.ca/snr/SNRcat/})
%     \item \cite{hips} -- Hierarchical progressive surveys (HIPS) (\url{http://aladin.u-strasbg.fr/hips/})
%     \item \cite{aladin-lite} -- Aladin Lite: Embed your Sky in the Browser (\url{http://aladin.u-strasbg.fr/AladinLite/})
%     \item 3FGL interactive table - (\url{http://fermi.gsfc.nasa.gov/ssc/data/access/lat/4yr_catalog/3FGL-table/})
%     \item \cite{hgps} -- H.E.S.S. Galactic plane survey (HGPS) -- upcoming TeV maps and catalog we will add.
% \end{itemize}
